---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Reading in the dataset from included .zip file from clone:

```{r}
activity <- read.csv(unz("activity.zip","activity.csv"), stringsAsFactors=FALSE, header=T, sep=",")

```

Aggregating steps by date:

```{r}
steps<-aggregate(steps ~ date, data=activity, sum)
````

## Histogram of steps
Using hist to graph a histogram of the number of steps:

```{r}
hist(steps$steps, main="Histogram of Steps", xlab="Steps")

```


## What is mean total number of steps taken per day?
```{r}
mean(steps$steps)
```
## What is the median total number of steps taken per day?
```{r}
median(steps$steps)
```



## What is the average daily activity pattern?
Aggregating data by intervals:
```{r}
steps2<-aggregate(steps ~ interval, data=activity, sum)
```
Averaging out over the number of days:
```{r}
steps2$stepsavg<-steps2$steps / nrow(steps)
```

Plotting the timeseries of the average daily activity:
```{r}
plot(x=steps2$interval, y=steps2$stepsavg, type="l", xlab="5 Minute Time Interval", ylab="Average Number of Steps", main="Average Number of Steps Taken\nAveraged Across All Days ")
```

Getting the max interval averaged out over all days:
```{r}
stepssorted<-steps2[order(steps2$stepsavg),]
tail(stepssorted, n=1)

```

## Imputing missing values
Calculating the number of NA values in steps for the activity DF:
```{r}
sum(is.na(activity$steps))
```




## Are there differences in activity patterns between weekdays and weekends?
